Behavior Driven Development in Haskell

### 2012-05-30 paper.tex
let "make" work.
supply "in Haskell".

\begin{itemize}
\item
    We originally implemented Doctest, back in 2010.
\item
    Add support for QuickCheck properties to Doctest (Section
    \ref{sec:user-doc} and Section \ref{sec:doctest})

@@

\noindent All combinators introduced in \ref{} have been
implemented~\cite{TODO}; and they will be incorporated into a future
release of Hspec.
The implementation is trivial, so we will not further discuss it.

>>>>

\begin{itemize}
\item
    We originally implemented Doctest in Haskell, back in 2010.
\item
    Add support for QuickCheck properties to Doctest (Section
    \ref{sec:user-doc} and Section \ref{sec:doctest})

@@

\noindent All combinators introduced in \ref{} have been
implemented~\cite{todo}; and they will be incorporated into a future
release of Hspec.
The implementation is trivial, so we will not further discuss it.
